% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Publications}{}

\begin{projects}
	\publication
    {\textbf{Thin Bridges for Drug Text Alignment: Lightweight Contrastive Learning for Target Specific Drug Retrieval} \underline{Mallikarjuna Tupakula}. \textit{NeurIPS 2025 2nd Workshop on Multi-modal Foundation Models and Large Language Models for Life Sciences (\textbf{NeurIPS'25 FM4LS}})} 
    \publication
    {\textbf{Quantifying the Academic Quality of Children’s Videos Using Machine Comprehension},  Sumeet Kumar, \underline{Mallikarjuna Tupakula}, Ashique KhudaBukhsh. \textit{INFORMS Journal on Computing} \textbf{Accepted} at \textbf{(IJOC)}}
    \publication
    {\textbf{Gender Biases and Stereotyping in Children’s Videos: A Study on 100 Popular Kids Channels on YouTube.}, Sumeet Kumar, \underline{Mallikarjuna Tupakula}, Ashique KhudaBukhsh. \textit{submitting to Nature Human Behaviour}\textbf{(Accepted at Association for Computational Linguistics \textbf{(ACL SRW’23)}}}
    \publication
    {\textbf{Anonymous Dissent in the Digital Age: A YouTube Dislikes Dataset.}Sujan Dutta, \underline{Mallikarjuna Tupakula}, Sumeet Kumar, Ashique KhudaBukhsh. \textit{The 16th International Conference on Advances in Social Networks Analysis and Mining}\textbf{(Accepted)}}
    \publication
    {\textbf{Large Language Models for Rating the Language of Children’s Videos on YouTube.} \underline{Mallikarjuna Tupakula}, Sumeet Kumar, Ashique KhudaBukhsh. INFORMS Journal on Computing \textit{(Submitting to IJOC)}}
    \publication
    {\textbf{Do Vision Transformers and Convolutional Neural Networks fit together?} \underline{Mallikarjuna Tupakula}\textit{Under Conference Submission}} 
    % \publication
    % {\textbf{Gender Stereotyping in Popular Children’s Videos.} Tiasa Singha Roy, \underline{Mallikarjuna Tupakula}, Sumeet Kumar, Ashique KhudaBukhsh.\textit{Annual Conference of the Association for Computational Linguistics \textbf{(ACL SRW’23)}}}
\end{projects}